---
title: "Data Analysis on Students' Technology Acceptance of Moodle and Academic Discipline"
author: "Laura Reinhardt"
date: "2024-04-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Analysis on Students' Technology Acceptance of Moodle and Academic Discipline


```{r data}
#install.packages("here")
library(here)
here()
data <- read.csv2(here("data", "data_tastudents.csv"), encoding="UTF-8", fileEncoding="latin1")
```
I have read in the data after having manually deleted unnecessary columns via Excel (time spent per page, and so on.)

```{r dimensions}
dim(data)
str(data)
```

```{r NA}
anyNA(data) # no initial NA values

for (i in 1:nrow(data)) { # loop through all rows and columns to replace empty values that are coded as -9 as actual NA that are recognized by R
  for (j in 1:ncol(data)) {
    if (data[i, j] == -9) {
      data[i, j] <- NA
    }
  }
}
```

```{r}
anyNA(data)
colSums(is.na(data))
```
One person didn't select what type of degree they are pursuing, two people did not select their gender and one person did not disclose their age. Since I cannot afford to lose their other replies, I will add an extra level "other" to these three columns. First, of course, I have to change the class of the columns to factors first.

```{r column_names}
colnames(data)[1] <- "ID"
colnames(data)
```
First, I changed the name of the first column to ID, since the name seems to have gotten corrupted during the import process.

```{r}
str(data)
```
```{r}
data$AD01 <- factor(data$AD01)
data$AD02 <- factor(data$AD02)
data$AD03 <- factor(data$AD03)
data$AU01_01 <- factor(data$AU01_01)
data$AU01_02 <- factor(data$AU01_02)
data$AU01_03 <- factor(data$AU01_03)
data$AU02 <- factor(data$AU02)
data$DE02 <- factor(data$DE02)
data$DE03 <- factor(data$DE03)

str(data)
```
 
Now I will treat the missing data that was previously found. NA are in the columns AD02, DE02 and DE03

```{r}
levels(data$AD02) <- c(levels(data$AD02), "Other")
levels(data$DE02) <- c(levels(data$DE02), "Other")
levels(data$DE03) <- c(levels(data$DE03), "Other")

data$AD02[is.na(data$AD02)] <- "Other"
data$DE02[is.na(data$DE02)] <- "Other"
data$DE03[is.na(data$DE03)] <- "Other"

colSums(is.na(data))
```
The missing data has been successfully dealt with.
